\documentclass[main.tex]{subfiles}
\begin{document}
  \section{Conclusion}
    The model’s predictions 78 percent of the time are either 1st or 2nd choice and 46 percent of the time the predictions are completely accurate. In volleyball quite often there is not much difference between top two choices as the final factor is often situational and takes into account where the block is at that moment. This means the model can be considered as a rather reliable model and introduces various uses. The model can easily be upgraded by introducing opponents block as a factor along with various strategies to avoid it which will fine tune the setter’s decisions even further. A great example is pipe attack which makes use of it. This model can serve very well as educational template for both professional and non-professional teams. The non-professional teams can use it to teach their setter what decisions to make in what situations. By simulating a specific situation in the model, the unexperienced setter can find out what type of sets are most lucrative in that position, how easy the set is and what should be his mean distribution among the positions from that position. This way the learning curve and greatly be increased by utilising decades of experience a professional setter would have. In professional teams the model can be used to increase the efficiency of their own setter. By recording his past sets and feeding them into the model for comparison. Certain positions can be more successful if set from a specific location other not so much. The setter can work then on limiting his unsuccessful choices and focus on increasing his successful options, once the block factor would be added to the model it would make an even stronger tool. This process can be reversed for analysing opponent’s team by finding from which position it is the most difficult to set from and then serve on that side to limit setter’s options or to see which positions is the most favourable to set to from specific area in the court. This can be a great tool to develop blocking strategies against specific teams and increase overall effectiveness of blocking decisions. Lastly gaming industry could make the use of this model for developing their AI as at the moment there have not been many games out there and a lot of them are clearly undeveloped compared to other sport games. 
\end{document}